---
title: "36-315-Lab3"
subtitle: ""  
author: "Meghan Hall"
date: 
output:
  xaringan::moon_reader:
    seal: false
    css: ["xaringan-themer.css", "custom.css"]
    lib_dir: libs
    nature:
      titleSlideClass: ["left", "middle"]
      highlightStyle: github
      highlightLines: true
      highlightSpans: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
---
```{r setup, include=FALSE}
library(emo)
#library(icons)
library(kableExtra)
#library(betweenthepipes)
library(tidyverse)
library(ggbeeswarm)
library(scales)
library(showtext)
options(knitr.kable.NA = '')
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
knitr::opts_chunk$set(fig.retina = 3, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.path = "figs/Lab1/")

font_add_google(name = "Open Sans",   # Name of the font on the Google Fonts site
                family = "open_sans")
font_add_google(name = "Source Serif Pro",   # Name of the font on the Google Fonts site
                family = "source_serif_pro")
showtext_auto()

cmu_theme <- function () { 
  theme_linedraw(base_size=11, base_family="source_serif_pro") %+replace% 
    theme(
      panel.background  = element_blank(),
      plot.background = element_rect(fill = "transparent", color = NA), 
      legend.background = element_rect(fill = "transparent", color = NA),
      legend.key = element_rect(fill = "transparent", color = NA),
      axis.ticks = element_blank(),
      panel.grid.major = element_line(color = "grey90", size = 0.3), 
      panel.grid.minor = element_blank(),
      plot.title = element_text(size = 18, hjust = 0, vjust = 0.5, face = "bold", margin = margin(b = 0.2, unit = "cm")),
      plot.subtitle = element_text(size = 12, hjust = 0, vjust = 0.5, margin = margin(b = 0.2, unit = "cm")),
      plot.caption = element_text(size = 7, hjust = 1, face = "italic", margin = margin(t = 0.1, unit = "cm")),
      axis.text.x = element_text(size = 13),
      axis.text.y = element_text(size = 13)
    )
}

```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)

style_mono_accent(
  header_font_google = google_font("Open Sans"),
  text_font_google   = google_font("Source Serif Pro", "400", "400i"),
  code_font_google   = google_font("Roboto Mono"),
  link_color = "#bb0000",
  base_color = "#bb0000",
  extra_fonts = list(
    google_font("Lato")
  ),
  extra_css = list(
    ".title-slide h2" = list("font-family" = "Source Serif Pro"),
    ".title-slide h3" = list("font-family" = "Source Serif Pro")
  )
)
```

class: inverse, center, middle

# 36-315: Statistical Graphics and Visualization
## Lab 3

Meghan Hall <br> Department of Statistics & Data Science <br> Carnegie Mellon University <br> June 1, 2021

---
layout: true
<div class="my-footer"><span>cmu-36315.netlify.app</span></div>
---

# Today

<br>

.large[More practice]
<br>
<br>
<br>
.large[Details with bar charts]
<br>
<br>
<br>
.large[Visualizing distributions]

---

# Adding extra info efficiently

.medium[Adding info to axis]

```{r custom, eval = FALSE}
# move the custom axis to x or y
mutate(custom_axis = paste0(judge, "\n", n, " episodes"))
```

<br>
--

.medium[Highlighting a certain group]

```{r highlight, eval = FALSE}
# move the highlight variable to fill
mutate(highlight_2013 = ifelse(year == 2013, 
                                 "highlight", "normal"))
```

---

# Lollipop chart

```{r lollipop, echo = FALSE, fig.align = "center"}
txhousing %>% 
  filter(month == 1 & year == 2015) %>% 
  ggplot(aes(y = city, x = median)) +
  geom_segment(aes(y = reorder(city, median), 
                   yend = reorder(city, median), x = 0, xend = median)) +
  geom_point(color = "red", size = 2.5) + 
  scale_x_continuous(labels = dollar) +
  labs(title = "Median home price in January 2015",
       y = "")
```

---

# Lollipop chart

<br>
<br>

.medium[Effective when you're comparing many categories]

<br>
<br>

.medium[Use a combination of `geom_segment` to draw the lines and `geom_point` to mark the ends]

---

# Comparing distributions

<br>

.medium[Box plots]

<br>

.medium[Violin plots]

<br>

.medium[Ridgeline plots]

<br>

.medium[**Beeswarm plots**]

---

# Beeswarm plot

```{r beeswarm, echo = FALSE, fig.align = "center"}
txhousing %>% 
  filter(year >= 2010) %>% 
  ggplot(aes(x = as.character(year), y = median)) +
  geom_beeswarm(size = 0.2, alpha = 0.5) +
  scale_y_continuous(labels = dollar)
```

---

# Beeswarm plot

<br>
<br>

.medium[Uses *smart* jittering]

<br>

.medium[Useful when there are few enough data points to see them all]

<br>

.medium[Needs `ggbeeswarm`]

---

# Upcoming

<br>

.large[Lab assignment due 11:30am EDT Wednesday!]
<br>
.medium[Ask questions on Piazza if they don't get answered here]

<br>

.large[Lecture 5 on Wednesday June 2]
<br>
.medium[Line charts and working with time]

<br>

.large[Graphic critique]
<br>
.medium[Follow instructions on syllabus, due before midterm]
