---
title: "36-315-Lec11"
subtitle: ""  
author: "Meghan Hall"
date: 
output:
  xaringan::moon_reader:
    seal: false
    css: ["xaringan-themer.css", "custom.css"]
    lib_dir: libs
    nature:
      titleSlideClass: ["left", "middle"]
      highlightStyle: github
      highlightLines: true
#      highlightSpans: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
---
```{r setup, include=FALSE}
library(emo)
#library(icons)
library(kableExtra)
#library(betweenthepipes)
library(tidyverse)
library(showtext)

options(knitr.kable.NA = '')
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
knitr::opts_chunk$set(fig.retina = 3, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.path = "figs/Lec10/")

font_add_google(name = "Open Sans",   # Name of the font on the Google Fonts site
                family = "open_sans")
font_add_google(name = "Source Serif Pro",   # Name of the font on the Google Fonts site
                family = "source_serif_pro")
showtext_auto()

cmu_theme <- function () { 
  theme_linedraw(base_size=11, base_family="source_serif_pro") %+replace% 
    theme(
      panel.background  = element_blank(),
      plot.background = element_rect(fill = "transparent", color = NA), 
      legend.background = element_rect(fill = "transparent", color = NA),
      legend.key = element_rect(fill = "transparent", color = NA),
      axis.ticks = element_blank(),
      panel.grid.major = element_line(color = "grey90", size = 0.3), 
      panel.grid.minor = element_blank(),
      plot.title = element_text(size = 18, hjust = 0, vjust = 0.5, face = "bold", margin = margin(b = 0.2, unit = "cm")),
      plot.subtitle = element_text(size = 12, hjust = 0, vjust = 0.5, margin = margin(b = 0.2, unit = "cm")),
      plot.caption = element_text(size = 7, hjust = 1, face = "italic", margin = margin(t = 0.1, unit = "cm")),
      axis.text.x = element_text(size = 13),
      axis.text.y = element_text(size = 13)
    )
}

```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)

style_mono_accent(
  header_font_google = google_font("Open Sans"),
  text_font_google   = google_font("Source Serif Pro", "400", "400i"),
  code_font_google   = google_font("Roboto Mono"),
  link_color = "#bb0000",
  base_color = "#bb0000",
  extra_fonts = list(
    google_font("Lato")
  ),
  extra_css = list(
    ".title-slide h2" = list("font-family" = "Source Serif Pro"),
    ".title-slide h3" = list("font-family" = "Source Serif Pro")
  )
)
```

class: inverse, center, middle

# 36-315: Statistical Graphics and Visualization
## Lecture 11

Meghan Hall <br> Department of Statistics & Data Science <br> Carnegie Mellon University <br> June 16, 2021

---
layout: true
<div class="my-footer"><span>cmu-36315.netlify.app</span></div>
---

# From last time

<br>

.large[Extensions to `ggplot2`]
<br>
.medium[in addition to the ones we've already covered]

<br>

.large[New plot types *and* new techniques for details]

---

# Today

<br>

.large[Different lecture than usual!]
<br>

<br>

.large[Midterm logistics & tips]
<br>
.medium[expectations for plots]

<br>

.large[Live coding with a new dataset]
<br>
.medium[with questions]

---

# Midterm logistics

<br>

.large[Available at 5pm Wednesday, due 5am Friday]
<br>
.medium[**EDT**]

<br>

.large[Logistically works like a homework assignment]
<br>
.medium[submit on Gradescope]

<br>

.large[Data source]
<br>
.medium[files on Canvas are a last resort]

---

.left[# Midterm logistics]

.pull-left[

### Allowed

<br>

Class materials

<br>

Notes

<br>

Documentation/resources

]

--

.pull-left[

### Not allowed

<br>

Piazza

<br>

Talking with classmates

<br>

Talking with *anyone* about the exam*

]

---

# You're prepared if...

<br>
<br>
.large[You've watched/attended lectures]

<br>
<br>

.large[You understand the lab/homework questions]

<br>
<br>

.large[You're familiar with viewing documentation & how to debug]

---

.left[# Data manipulation techniques]

.center[**non-exhaustive list**]

.pull-left[
<br>
<br>
.large[Creating new variables]
<br>
.medium[maybe with `paste0` to create strings]<br>

<br>

.large[Aggregating data]
<br>
.medium[`group_by` + `summarize`]<br>
]

.pull-right[
<br>
<br>
.large[Joining with `left_join`]
<br>
.medium[maybe with two key variables instead of just one]<br>

<br>

.large[Pivoting data]
<br>
.medium[`pivot_wider` and `pivot_longer`]<br>
]

---

# Overall tips

.large[Take time to look at your data first]
<br>

<br>

.large[Remember you can control variable type]
<br>
.medium[with `as.character` and `as.numeric`]<br>

<br>

.large[Notice what rates are being asked for]
<br>
.medium[like with the TB case rates in HW 3]<br>

<br>

.large[Remember there are multiple solutions!]
<br>
.medium[we've covered different ways to relabel values, highlight points, annotate graphs, etc.]<br>

---

.left[# Guidelines for plots]

.pull-left[
.large[Follow the guidelines we've discussed]
<br>
.medium[everything must be readable, etc.]<br>

<br>

.large[Use appropriate color scales]
<br>

<br>

.large[Use a good, explanatory title]
<br>
]

.pull-right[
.large[If you need a legend, make it look nice]
<br>

<br>

.large[Order bars/geoms in an appropriate fashion]
<br>

<br>

.large[Use appropriate axis titles]
]

---

# Schedule

<br>

.large[Midterm available at 5pm today, due 5am Friday]

<br>

.large[Homework 4 due Tuesday June 22]

<br>

.large[Will start discussing final projects next week]

---

class: inverse, center, middle

# To RStudio!