---
title: "36-315-Lab4"
subtitle: ""  
author: "Meghan Hall"
date: 
output:
  xaringan::moon_reader:
    seal: false
    css: ["xaringan-themer.css", "custom.css"]
    lib_dir: libs
    nature:
      titleSlideClass: ["left", "middle"]
      highlightStyle: github
      highlightLines: true
      highlightSpans: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
---
```{r setup, include=FALSE}
library(emo)
#library(icons)
library(kableExtra)
#library(betweenthepipes)
library(tidyverse)
library(lubridate)
library(showtext)
options(knitr.kable.NA = '')
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
knitr::opts_chunk$set(fig.retina = 3, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.path = "figs/Lab1/")

font_add_google(name = "Open Sans",   # Name of the font on the Google Fonts site
                family = "open_sans")
font_add_google(name = "Source Serif Pro",   # Name of the font on the Google Fonts site
                family = "source_serif_pro")
showtext_auto()

cmu_theme <- function () { 
  theme_linedraw(base_size=11, base_family="source_serif_pro") %+replace% 
    theme(
      panel.background  = element_blank(),
      plot.background = element_rect(fill = "transparent", color = NA), 
      legend.background = element_rect(fill = "transparent", color = NA),
      legend.key = element_rect(fill = "transparent", color = NA),
      axis.ticks = element_blank(),
      panel.grid.major = element_line(color = "grey90", size = 0.3), 
      panel.grid.minor = element_blank(),
      plot.title = element_text(size = 18, hjust = 0, vjust = 0.5, face = "bold", margin = margin(b = 0.2, unit = "cm")),
      plot.subtitle = element_text(size = 12, hjust = 0, vjust = 0.5, margin = margin(b = 0.2, unit = "cm")),
      plot.caption = element_text(size = 7, hjust = 1, face = "italic", margin = margin(t = 0.1, unit = "cm")),
      axis.text.x = element_text(size = 13),
      axis.text.y = element_text(size = 13)
    )
}

```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)

style_mono_accent(
  header_font_google = google_font("Open Sans"),
  text_font_google   = google_font("Source Serif Pro", "400", "400i"),
  code_font_google   = google_font("Roboto Mono"),
  link_color = "#bb0000",
  base_color = "#bb0000",
  extra_fonts = list(
    google_font("Lato")
  ),
  extra_css = list(
    ".title-slide h2" = list("font-family" = "Source Serif Pro"),
    ".title-slide h3" = list("font-family" = "Source Serif Pro")
  )
)
```

class: inverse, center, middle

# 36-315: Statistical Graphics and Visualization
## Lab 4

Meghan Hall <br> Department of Statistics & Data Science <br> Carnegie Mellon University <br> June 3, 2021

---
layout: true
<div class="my-footer"><span>cmu-36315.netlify.app</span></div>
---

# Today

<br>

.large[Creating line graphs]
<br>
.medium[pivoting data]
<br>
.medium[labeling with `ggrepel`]
<br>
.medium[using functions from `lubridate`]
<br>
<br>
.large[Instructions]
<br>
.medium[HW: describe the graphs]
<br>
.medium[HW/labs: add plot title and relevant axis titles (include units!)]

---

# `pivot_longer`

**need to pivot when your data is at a different observation level than necessary for analysis/visualization**<br>
data here is by track, we need observations per week

```{r pivot-1, echo = FALSE}
billboard %>% 
  filter(artist == "Dixie Chicks, The") %>% 
  select(artist, track, wk1:wk3) %>% 
  kable("html") %>%
  kable_styling(font_size = 16, position = "center", full_width = F) %>%
  row_spec(0, bold = T, color = "white", background = "#bb0000")
```

---

# `pivot_longer`

**need to pivot when your data is at a different observation level than necessary for analysis/visualization**<br>
data here is by track, we need observations per week

```{r pivot-2, eval = FALSE}
billboard %>% 
  filter(artist == "Dixie Chicks, The") %>% 
  select(artist, track, wk1:wk3) %>% 
  pivot_longer(wk1:wk3, names_to = "week", values_to = "ranking") #<<
```

--

```{r pivot-3, echo = FALSE}
billboard %>% 
  filter(artist == "Dixie Chicks, The") %>% 
  select(artist, track, wk1:wk3) %>% 
  pivot_longer(wk1:wk3, names_to = "week", values_to = "ranking") %>% 
  head(6) %>% 
  kable("html") %>%
  kable_styling(font_size = 16, position = "center", full_width = F) %>%
  row_spec(0, bold = T, color = "white", background = "#bb0000")
```

---

# Options for relabeling

**`fct_recode` is useful when you have a factor and ordering is important**

```{r recode-1, eval = FALSE}
# from Wednesday's lecture
mutate(qround = fct_recode(qround, "Qualifying 1" = "q1",
                           "Qualifying 2" = "q2", 
                           "Qualifying 3" = "q3")
```

--

**`case_when` is generally easier when you have a standard categorical variable**

```{r recode-2, eval = FALSE}
# example from mpg data set
mutate(drv = case_when(drv == "f" ~ "front-wheel drive",
                       drv == "r" ~ "rear-wheel drive",
                       drv == "4" ~ "four-wheel drive"))
```

---

# Dealing with dates

**functions from `lubridate`**

```{r date-1, eval = FALSE}
# from Wednesday's lecture
mutate(time_format = ms(time),
       seconds = seconds(time_format))

# from today's lab
mutate(date = ym(paste(year, month)))
```

--

**special scale when axis is a date**

```{r date-2, eval = FALSE}
scale_x_date(date_breaks = "1 year",
             date_labels = "%m-%Y")
```

--

```{r date-3, echo = FALSE, fig.align = "center", fig.height = 2}
txhousing %>% 
  filter(year >= 2010) %>% 
  mutate(date = ym(paste(year, month))) %>% 
  ggplot(aes(x = date)) +
  scale_x_date(date_breaks = "1 year",
               date_labels = "%m-%Y")
```

---

# Upcoming

<br>

.large[Lab assignment due 11:30am EDT Friday!]
<br>
.medium[Ask questions on Piazza if they don't get answered here]

<br>

.large[Lecture 6 on Friday June 3]
<br>
.medium[Scatter plots]

<br>

.large[Homework 2 due 11:30am EDT Tuesday]
<br>
.medium[Posted now]
