---
title: "36-315-Lab2"
subtitle: ""  
author: "Meghan Hall"
date: 
output:
  xaringan::moon_reader:
    seal: false
    css: ["xaringan-themer.css", "custom.css"]
    lib_dir: libs
    nature:
      titleSlideClass: ["left", "middle"]
      highlightStyle: github
      highlightLines: true
      highlightSpans: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
---
```{r setup, include=FALSE}
library(emo)
#library(icons)
library(kableExtra)
#library(betweenthepipes)
library(tidyverse)
library(showtext)
options(knitr.kable.NA = '')
options(htmltools.dir.version = FALSE, htmltools.preserve.raw = FALSE)
knitr::opts_chunk$set(fig.retina = 3, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.path = "figs/Lab1/")

font_add_google(name = "Open Sans",   # Name of the font on the Google Fonts site
                family = "open_sans")
font_add_google(name = "Source Serif Pro",   # Name of the font on the Google Fonts site
                family = "source_serif_pro")
showtext_auto()

cmu_theme <- function () { 
  theme_linedraw(base_size=11, base_family="source_serif_pro") %+replace% 
    theme(
      panel.background  = element_blank(),
      plot.background = element_rect(fill = "transparent", color = NA), 
      legend.background = element_rect(fill = "transparent", color = NA),
      legend.key = element_rect(fill = "transparent", color = NA),
      axis.ticks = element_blank(),
      panel.grid.major = element_line(color = "grey90", size = 0.3), 
      panel.grid.minor = element_blank(),
      plot.title = element_text(size = 18, hjust = 0, vjust = 0.5, face = "bold", margin = margin(b = 0.2, unit = "cm")),
      plot.subtitle = element_text(size = 12, hjust = 0, vjust = 0.5, margin = margin(b = 0.2, unit = "cm")),
      plot.caption = element_text(size = 7, hjust = 1, face = "italic", margin = margin(t = 0.1, unit = "cm")),
      axis.text.x = element_text(size = 13),
      axis.text.y = element_text(size = 13)
    )
}

```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)

style_mono_accent(
  header_font_google = google_font("Open Sans"),
  text_font_google   = google_font("Source Serif Pro", "400", "400i"),
  code_font_google   = google_font("Roboto Mono"),
  link_color = "#bb0000",
  base_color = "#bb0000",
  extra_fonts = list(
    google_font("Lato")
  ),
  extra_css = list(
    ".title-slide h2" = list("font-family" = "Source Serif Pro"),
    ".title-slide h3" = list("font-family" = "Source Serif Pro")
  )
)
```

class: inverse, center, middle

# 36-315: Statistical Graphics and Visualization
## Lab 2

Meghan Hall <br> Department of Statistics & Data Science <br> Carnegie Mellon University <br> May 27, 2021

---
layout: true
<div class="my-footer"><span>cmu-36315.netlify.app</span></div>
---

# Today

<br>

.large[Reviewing bar charts]
<br>
.medium[]

---

# Standard bar chart

```{r standard, eval = FALSE}
got %>% 
  ggplot(aes(x = region)) +
  geom_bar()
```

<br>

.medium[If you don't have a variable on the `y` aesthetic, you don't need a `stat` argument]

<br>

.medium[If you *do* have a variable on the `y` aesthetic (whether a count, aggregate, or other data), you need the `stat  = "identity"` argument within `geom_bar()`]

---

# Grouped bar chart

```{r grouped, eval = FALSE}
got %>%
  ggplot(aes(x = attacker_king, fill = battle_type)) + 
  geom_bar(position = "dodge")
```

<br>

.medium[The `position = "dodge"` argument within `geom_bar()` will create a grouped bar chart, as long as you have a `fill` aesthetic]

---

# Stacked bar chart

```{r stacked, eval = FALSE}
got %>% 
  ggplot(aes(x = attacker_king, fill = region)) + 
  geom_bar(position = "stack")
```

<br>

.medium[The `position = "stack"` argument within `geom_bar()` will create a stacked bar chart, as long as you have a `fill` aesthetic]

<br>

.medium[Be careful using this chart type with a `fill` variable that has too many levels, as it's hard to compare]

---

# Percent stacked bar chart

```{r percent, eval = FALSE}
got %>% 
  add_count(attacker_king) %>%
  ggplot(aes(x = attacker_king, y = n, fill = attacker_outcome)) +
  geom_bar(stat = "identity", position = "fill")
```

<br>

.medium[The `position = "fill"` argument within `geom_bar()` will create a percent stacked bar chart, as long as you have a `fill` aesthetic and a summary variable on the `y` aesthetic]

---

# Upcoming

<br>

.large[Lab assignment due 11:30am EDT Friday!]
<br>
.medium[Ask questions on Piazza if they don't get answered here]

<br>

.large[Lecture 4 on Friday May 28]
<br>
.medium[Histograms and box plots]

<br>

.large[Homework 1 due Tuesday June 1]
<br>
.medium[Will be posted soon]
